### 2020-07-16 code/figure4.Rmd

```{r figure-4, message = FALSE, fig.cap="**Figure 4: Some genes with multiple pathway memberships drive clustering.** Each column is a tumor in class 6 or 7, each row represents a gene with mutation (red) or not mutated (grey). The genes are organized according to which of the top distinguishing pathways for this class that they effect. Some genes affect multiple pathways, as indicated by the bars at left. The highlighted genes at right are all proteasomal subunits.", eval=FALSE}

load("../data/class67_gene_2_path_heatmap.Rda") ## load data
load("../data/path_match_in_set.Rda")

>>>>

```{r child = '../code/figure4_function.Rmd'}

```{r figure-4-oncoprint, message = FALSE, fig.cap="**Figure 4: Some genes with multiple pathway memberships drive clustering.** Each column is a tumor in class 6 or 7, each row represents a gene with mutation (red) or not mutated (grey). The genes are organized according to which of the top distinguishing pathways for this class that they effect. Some genes affect multiple pathways, as indicated by the bars at left. The highlighted genes at right are all proteasomal subunits."}

class67 <- oncoprint_style(filtered_class = c(6,7), n_path = 10)
class67
```

```{r figure-4, message = FALSE, fig.cap="**Figure 4: Some genes with multiple pathway memberships drive clustering.** Each column is a tumor in class 6 or 7, each row represents a gene with mutation (red) or not mutated (grey). The genes are organized according to which of the top distinguishing pathways for this class that they effect. Some genes affect multiple pathways, as indicated by the bars at left. The highlighted genes at right are all proteasomal subunits.", eval = FALSE}
load("../data/class67_gene_2_path_heatmap.Rda") ## load data
load("../data/path_match_in_set.Rda")

### 2020-07-16 code/table1.Rmd

```{r table-1}
load("../data/cluster_spec_enrich_table1.Rda")
cluster_spec_enrich_table1 %>% kable(caption = "Table 1: Most mutated gene in class-specific pathways (enrichment score >= 0.30) for specific cancer", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = T)
```

>>>>

```{r table-1}
load("../data/cluster_spec_enrich_table1.Rda")
tumor_clusters <- fread("../data/umap_2d_3d_coors.tsv") ## load in data

## Selecting the top 10 cancers with the largest n for table 1
n_tumor <- as.data.frame(table(tumor_clusters$project_code))
n_tumor <- n_tumor %>% arrange(desc(Freq)) %>% .[1:10, "Var1"] %>% as.character() %>% .[order(.)]

cluster_spec_enrich_table1 %>% .[, c("Pathway", "Class", n_tumor)] %>% kable(caption = "Table 1: Most mutated gene in class-specific pathways (enrichment score >= 0.30) for specific cancer", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = T)
```
<p style="FONT-SIZE:10px; COLOR:#000000; LINE-HEIGHT:12px;">**Table 1:** The numbers in this table are completely wrong, it is just a place holder, please ignore</p>
